\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-11-08 chapters/supplementary.tex
Add spectral exp; update Cityscapes sec. and App.

@@

\begin{algorithm}
  \caption{Implementation of \algname{}, generalized algorithm for signed graph partitioning}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges; boolean \texttt{{\color{blue}addCannotLinkConstraints}} \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State $\tilde{\mathcal{G}}(\tilde{V},\tilde{E}) \gets \mathcal{G}(V,E,w^+,w^-)$  \Comment{Init. contracted graph}
      \State \texttt{UF} $\gets$ initUnionFind($V$) \Comment{Init. data structure representing clustering}
        \State PQ.push$(|w_e|, e) \quad \forall e \in E $  \Comment{Init. priority queue in desc. order of $|w_e|=|w_e^+ - w_e^-|$, $\mathcal{O}(|E|)$}
        \State \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$ \Comment{Init. cannot-link constraints}
    \State
      \While{PQ is \textbf{not} empty}
        \State $\tilde{w}, e_{uv} \gets $ PQ.popHighest() \Comment{$\mathcal{O}(\log |E|)$}
        \State \textbf{assert} \texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$) \Comment{Edges in PQ always link nodes in different clusters}
        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
          \State PQ, \texttt{canBeMerged}, $\tilde{E}$ $\gets$ \textsc{UpdateNeighbors}($u,v$)
          \State $\tilde{V} \gets \tilde{V} \setminus \{ v\}$, $\quad \tilde{E} \gets \tilde{E} \setminus \{ e_{uv}\}$ \Comment{Update contracted graph}
          \State \texttt{UF}.merge($u,v$) \Comment{Merge clusters, $\mathcal{O}(\alpha(|E|))$}
        \ElsIf{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False} \Comment{Constrain the two clusters}
        \EndIf
      \EndWhile
      \State
      \Return Final clustering given by union-find data structure  \texttt{UF}
  \end{algorithmic}
  \hspace*{1.5cm} 
    \begin{algorithmic}[1]
    \Function{UpdateNeighbors}{$u,v$}
      \State $\mathcal{N}_u = \{ t \in \tilde{V} | e_{ut}\in \tilde{E}  \}$
      \State $\mathcal{N}_v = \{ t \in \tilde{V} | e_{vt}\in \tilde{E}  \}$ 
      \For{$t \in \mathcal{N}_v$ } \Comment{Loop over neighbors in $\tilde{\mathcal{G}}$ of deleted node $v$}
        \State $\tilde{E} \gets \tilde{E} \setminus \{e_{vt}\}$
        \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{$\mathcal{O}(\log |E|)$}
        \State \texttt{canBeMerged}$[e_{ut}] \gets$ \texttt{canBeMerged}$[e_{ut}]$ \textbf{and} \texttt{canBeMerged}$[e_{vt}]$
        \If{$t \in \mathcal{N}_u$ }\Comment{$t$ is a common neighbor of $u$ and $v$}
          \State $\tilde{w}_{ut} \gets$ PQ.delete($e_{ut}$)  \Comment{$\mathcal{O}(\log |E|)$}
          \State PQ.push($ |f(\tilde{w}_{ut}, \tilde{w}_{vt})|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$  }
        \Else
          \State $\tilde{E} \gets \tilde{E} \cup \{e_{ut}\}$
          \State PQ.push($ |\tilde{w}_{vt}|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$}
        \EndIf
      \EndFor
      \State
      \Return PQ, \texttt{canBeMerged}, $\tilde{E}$
    \EndFunction
  \end{algorithmic}
  \label{detailed_alg}
\end{algorithm}
\begin{figure}
        \centering
\begin{minipage}{0.49\textwidth}
\centering
        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
    \end{minipage} \hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \scriptsize
                \begin{tabular}[b]{r | l }
            \toprule
            Linkage criteria & Update rule $f$ \\        
            \midrule
            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
            $
            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
            $}
               \\ 
            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
            Maximum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
            Minimum:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
        \end{tabular}
\end{minipage}
\caption{ 
\textbf{Left:} Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction. \textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}
\label{fig:edge_contraction_and_contr_graph}  
\end{figure}

@@

\paragraph*{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed, as shown in Algorithm \ref{main_alg}.  
An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph. Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that there exists exactly one representative $|\tilde{V} \cap S| = 1$ for every cluster $S \in \Pi$ . Edges in $\tilde{E}$ represent adjacency-relationships between clusters 
and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
\begin{equation}
  \interact(S_u \cup S_v,S_t) = f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
\end{equation}
In Fig. \ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.

@@

\begin{algorithm}
  \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State \texttt{UF} $\gets$ initUnionFind($V$) 
      \For{$(u,v)=e\in E$ in descending order of $|w_e|=|w_e^+ - w_e^-|$}
        \If{\texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$)} \Comment{Check if $u,v$ are already in the same cluster}
          \If{({\color{ForestGreen}\textbf{$w_e > 0$}}) \textbf{and} \texttt{canBeMerged}($u,v$)}  \Comment{Check for cannot-link constraints}
            \State \texttt{UF}.merge($u,v$) and inherit constraints of parent clusters
          \ElsIf{({\color{red}\textbf{$w_e \leq 0$}})}
            \State Add cannot-link constraints between parent clusters of $u,v$
          \EndIf
        \EndIf
      \EndFor
      \State
      \Return Final clustering given by union-find data structure \texttt{UF}
  \end{algorithmic}
  \label{alg:mutex_watershed}
\end{algorithm}

\subsection{Properties of \algname{} with \emph{Absolute Maximum} linkage}\label{sec:appendix_abs_max}
\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies. On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
\begin{align}
E^+ = \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\},& \qquad E^- = \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\} \\
W^+ = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},& \qquad W^- = \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}
\end{align}

@@

\begin{figure}
        \centering

        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters. Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
}
\label{fig:abs_max_proof_example}  
\end{figure}

\subsection{Predicting signed edge weights with a CNN}
Our CNN model outputs affinities in the form of pseudo-probabilities $p:E \rightarrow [0,1]$, where $p=0$ represents a boundary evidence. In order to use them as input of the algorithms in our framework, we mapped them to positive and negative values\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}. The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
\begin{equation} \label{eq:mappings}
\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right),
\end{equation}
where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation. We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage. Note that varying the parameter $\beta$ does not usually define a hierarchy of nested clusterings, thus it is not equivalent to varying a threshold parameter in HAC. This hierarchical property is only valid for \algname{} without constraints and with \emph{Average}, \emph{Max} or \emph{Min} linkage.

@@

\begin{table}[t]
\centering
    \footnotesize
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
    CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0$. We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.}
    \label{tab:extended_results_cremi}
\end{table}

@@

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
\begin{figure}[t]
\centering
\begin{minipage}[T]{0.6\textwidth}
\centering
        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
    \captionof{figure}{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise. (\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq. \ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$. Long-range predictions are not shown.
    }
    \label{fig:noisy_affs}
\end{minipage}\hfill
\begin{minipage}[T]{0.35\textwidth}
    \centering
    \footnotesize
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints}
    \label{tab:extended_results_cityscapes_val}
\end{minipage}
\end{figure}

>>>>

\begin{algorithm*}
  \caption{Implementation of \algname{}, generalized algorithm for signed graph partitioning}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges; boolean \texttt{{\color{blue}addCannotLinkConstraints}} \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State $\tilde{\mathcal{G}}(\tilde{V},\tilde{E}) \gets \mathcal{G}(V,E,w^+,w^-)$  \Comment{Init. contracted graph}
      \State \texttt{UF} $\gets$ initUnionFind($V$) \Comment{Init. data structure representing clustering}
        \State PQ.push$(|w_e|, e) \quad \forall e \in E $  \Comment{Init. priority queue in desc. order of $|w_e|=|w_e^+ - w_e^-|$, $\mathcal{O}(|E|)$}
        \State \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$ \Comment{Init. cannot-link constraints}
    \State
      \While{PQ is \textbf{not} empty}
        \State $\tilde{w}, e_{uv} \gets $ PQ.popHighest() \Comment{$\mathcal{O}(\log |E|)$}
        \State \textbf{assert} \texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$) \Comment{Edges in PQ always link nodes in different clusters}
        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
          \State PQ, \texttt{canBeMerged}, $\tilde{E}$ $\gets$ \textsc{UpdateNeighbors}($u,v$)
          \State $\tilde{V} \gets \tilde{V} \setminus \{ v\}$, $\quad \tilde{E} \gets \tilde{E} \setminus \{ e_{uv}\}$ \Comment{Update contracted graph}
          \State \texttt{UF}.merge($u,v$) \Comment{Merge clusters, $\mathcal{O}(\alpha(|E|))$}
        \ElsIf{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False} \Comment{Constrain the two clusters}
        \EndIf
      \EndWhile
      \State
      \Return Final clustering given by union-find data structure  \texttt{UF}
  \end{algorithmic}
  \hspace*{1.5cm} 
    \begin{algorithmic}[1]
    \Function{UpdateNeighbors}{$u,v$}
      \State $\mathcal{N}_u = \{ t \in \tilde{V} | e_{ut}\in \tilde{E}  \}$
      \State $\mathcal{N}_v = \{ t \in \tilde{V} | e_{vt}\in \tilde{E}  \}$ 
      \For{$t \in \mathcal{N}_v$ } \Comment{Loop over neighbors in $\tilde{\mathcal{G}}$ of deleted node $v$}
        \State $\tilde{E} \gets \tilde{E} \setminus \{e_{vt}\}$
        \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{$\mathcal{O}(\log |E|)$}
        \State \texttt{canBeMerged}$[e_{ut}] \gets$ \texttt{canBeMerged}$[e_{ut}]$ \textbf{and} \texttt{canBeMerged}$[e_{vt}]$
        \If{$t \in \mathcal{N}_u$ }\Comment{$t$ is a common neighbor of $u$ and $v$}
          \State $\tilde{w}_{ut} \gets$ PQ.delete($e_{ut}$)  \Comment{$\mathcal{O}(\log |E|)$}
          \State PQ.push($ |f(\tilde{w}_{ut}, \tilde{w}_{vt})|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$  }
        \Else
          \State $\tilde{E} \gets \tilde{E} \cup \{e_{ut}\}$
          \State PQ.push($ |\tilde{w}_{vt}|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$}
        \EndIf
      \EndFor
      \State
      \Return PQ, \texttt{canBeMerged}, $\tilde{E}$
    \EndFunction
  \end{algorithmic}
  \label{detailed_alg}
\end{algorithm*}

\begin{figure*}
        \centering
\begin{minipage}{0.49\textwidth}
\centering
        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
    \end{minipage} \hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \small
                \begin{tabular}[b]{r | l }
            \toprule
            Linkage criteria & Update rule $f$ \\        
            \midrule
            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
            $
            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
            $}
               \\ 
            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
            Maximum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
            Minimum:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
        \end{tabular}
\end{minipage}
\caption{ 
\textbf{Left:} Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction. \textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters.}
\label{fig:edge_contraction_and_contr_graph}  
\end{figure*}

@@

@@

\paragraph*{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed, as shown in Algorithm \ref{main_alg}.  
An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph. Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that there exists exactly one representative $|\tilde{V} \cap S| = 1$ for every cluster $S \in \Pi$ . Edges in $\tilde{E}$ represent adjacency-relationships between clusters 
and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can recompute these interactions by using an \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$:
\begin{align}
  \interact(S_u \cup S_v,S_t) =& f\Big[ \interact(S_u,S_t), \interact(S_v,S_t) \Big] \\
  =& f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) 
\end{align}
In Fig. \ref{fig:edge_contraction_and_contr_graph} we show an example of edge contraction and we list the update rules associated to the linkage criteria we introduced in Table \ref{tab:linkage-criteria}.

@@

\begin{algorithm*}
  \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State \texttt{UF} $\gets$ initUnionFind($V$) 
      \For{$(u,v)=e\in E$ in descending order of $|w_e|=|w_e^+ - w_e^-|$}
        \If{\texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$)} \Comment{Check if $u,v$ are already in the same cluster}
          \If{({\color{ForestGreen}\textbf{$w_e > 0$}}) \textbf{and} \texttt{canBeMerged}($u,v$)}  \Comment{Check for cannot-link constraints}
            \State \texttt{UF}.merge($u,v$) and inherit constraints of parent clusters
          \ElsIf{({\color{red}\textbf{$w_e \leq 0$}})}
            \State Add cannot-link constraints between parent clusters of $u,v$
          \EndIf
        \EndIf
      \EndFor
      \State
      \Return Final clustering given by union-find data structure \texttt{UF}
  \end{algorithmic}
  \label{alg:mutex_watershed}
\end{algorithm*}

\subsection{Properties of \algname{} with Absolute Maximum linkage}\label{sec:appendix_abs_max}
\paragraph{Remark on graph notation} The definition of a graph proposed by \cite{wolf2018mutex} makes a distinction between a set of positive edges $E^+$, associated with a set $W^+$ of positive scalar attributes representing merge affinities, and a set of negative edges $E^-$, associated with a set $W^-$ of positive attributes representing split tendencies. On the other hand, in our definition $\mathcal{G}(V,E,w^+,w^-)$ each edge have both an attractive $w_e^+$ and a repulsive $w_e^-$ attribute, so we can make them equivalent by defining:
\begin{align}
E^+ =&\,\, \{ e \in E \,\,\text{s.t.} \,\,w_e = w_e^+ - w_e^- > 0\}, \\
E^- =&\,\, \{ e \in E \,\,\text{s.t.}\,\, w_e = w_e^+ - w_e^- \leq 0\}, \\
W^+ =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^+\},\\
 W^- =&\,\, \{ |w_e| \,\,\text{s.t.}\,\, e \in E^-\}.
\end{align}

@@

\begin{figure*}
        \centering

        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters. Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
}
\label{fig:abs_max_proof_example}  
\end{figure*}

\subsection{Predicting signed edge weights with a CNN}
Our CNN model outputs affinities in the form of pseudo-probabilities $p:E \rightarrow [0,1]$, where $p=0$ represents a boundary evidence. In order to use them as input of the algorithms in our framework, we mapped them to positive and negative values\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}. The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
\begin{align} 
\cost_{e,\mathrm{Add}} =&\,\, p_e - \beta, \\
\cost_{e,\mathrm{Log}} =&\,\, \log \left( \frac{p_e}{1-p_e} \right) - \log \left( \frac{\beta}{1-\beta} \right), \label{eq:mappings}
\end{align}
where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation. We evaluated both of them empirically with each of the tested linkage and found that the additive mapping is the best option in all cases apart from the \emph{Sum} linkage. Note that varying the parameter $\beta$ does not usually define a hierarchy of nested clusterings, thus it is not equivalent to varying a threshold parameter in HAC. This hierarchical property is only valid for \algname{} without constraints and with \emph{Average}, \emph{Max} or \emph{Min} linkage.

@@

\begin{table*}[t]
\centering
    \footnotesize
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
    CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0$. We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.}
    \label{tab:extended_results_cremi}
\end{table*}

@@

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
\begin{figure*}[t]
\centering
\begin{minipage}[T]{0.61\textwidth}
\centering
        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
    \captionof{figure}{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise. (\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq. \ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$. Long-range predictions are not shown.
    }
    \label{fig:noisy_affs}
\end{minipage}\hfill
\begin{minipage}[T]{0.35\textwidth}
    \centering
    \small
    \vspace*{1.6em}
        \begin{tabular}{l|c|c}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \vspace*{0.5em}
    \captionof{table}{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints}
    \label{tab:extended_results_cityscapes_val}
\end{minipage}
\end{figure*}
